---
title: "Assignment-4"
author: "Yeswanth Siripurapu"
date: "2023-10-29"
output:
  pdf_document: default
  html_document: default
---
```{r}
Pharmaceuticals <- read.csv("D:/Pharmaceuticals.csv")
```

```{r}
library(tidyverse)# For Data manipulation

```

```{r}
library(factoextra)# Used for clustering algorithms and visualization

```

```{r}
library(dplyr)
library(ggplot2)
library(cluster)

```

```{r}
Pharma_data <- na.omit(Pharmaceuticals) 
#Provides the data after removing the incomplete cases.
Pharma_data


```

```{r}
#Taking the quantitative variables(1-9) to cluster the 21 firms
row.names(Pharma_data)<- Pharma_data[,1]
Pharma_data1<- Pharma_data[,3:11]
# Considering only numercial values i.e., 3-11 columns from csv file
head(Pharma_data1)

```
```{r}
#Normalizing the data frame with scale method
Pharma_data2<-scale(Pharma_data1)
head(Pharma_data2)
```
```{r}
#To determine the number of clusters to do the cluster analysis using Elbow Method
fviz_nbclust(Pharma_data2, kmeans, method = "wss")

```

```{r}
##By seeing the above graph from Elbow method, Graph is not 
#clear to choose k=2 or 3 or 4 or 5.
#Silhouette method for determining no of clusters


fviz_nbclust(Pharma_data2, kmeans, method = "silhouette")

```

```{r}
#Applying K-means
set.seed(64060)
k_5<- kmeans(Pharma_data2,centers=5,nstart = 25)

```

```{r}
#Visualizing the output
#centroids
k_5$centers

```
```{r}
fviz_cluster(k_5,data = Pharma_data2) # to Visualize the clusters

```

```{r}
k_5

```

```{r}

distance<- dist(Pharma_data2, method = "euclidean")
fviz_dist(distance)

```

```{r}
## I can see there are 5 clusters and the center is defined after 25 restarts
#which is determined in kmeans.
#K - Means Cluster Analysis- Fit the data with 5 clusters
fit<-kmeans(Pharma_data2,5)

```


```{r}
#Finding the mean value of all quantitative variables for each cluster
aggregate(Pharma_data2,by=list(fit$cluster),FUN=mean)

```

```{r}

##To view the cluster plot

clusplot(Pharma_data2,fit$cluster,color =
           TRUE,shade = TRUE,labels = 2,lines = 0)

```

#Task 2: Examine the clusters in light of the numerical variables that were utilised to create them.
#Cluster_1 - AGN, PHA, BAY - These have the highest PE_Ratio. #By observing the mean values of all quantitative variables for each cluster. The ROE value is poor.
#JNJ, MRK, GSK, and PFE are in #Cluster_2 and have the biggest market capitalization and good leverage value.
#AHM, AVE, and WPI are in #Cluster_3; they have the lowest beta and asset turnover.
#Cluster_4: The lowest market capitalization, leverage, and beta are exhibited by IVX, MRX, ELN, and CHTT.
#They're good. Its revenue growth is the highest.
#Cluster_5: ABT, NVS, AZN, LLY, BMY, WYE, SGP - These companies have the largest net profit margin, the biggest asset turnover, and the lowest sales growth.


#Task 3: Do the clusters exhibit any patterns in relation to the numerical variables (10–12)?
#(those not utilised in cluster formation)
#For cluster 1: It should be held in accordance with media recommendations as it has the highest PE Ratio.
#For cluster 2: It has a good leverage value and the largest market capitalization. Additionally, they can be rather violent#For cluster 3: Its beta and asset turnover are the lowest. However, media endorsements are very positive.#For cluster 4: They come with a modest recommendation despite the high leverage ratio.
#For Cluster 5: They have the largest net profit margin, the highest asset turnover, and the lowest revenue growth.


#Task 4: Using any or all of the variables in the dataset, give each cluster a suitable name.
#Cluster 1: Hold cluster – Their numbers are respectable.
#4 Cluster 2: Mild Purchase or Hold a cluster.
#Cluster 3: To Purchase or To Sell
#Cluster 4: Purchase Cluster; it is fairly stable.
#High Hold Cluster is Cluster # 5.








